---
title: "Homework 6"
subtitle: "EDLD 651"
author: "Haley Brown, Sabine Scott, Suzie Stadelman, & Emily Wilke"
format: pdf
execute: 
  eval: true
  echo: false
  warning: false
  error: false
fig-width: 6.5
fig-height: 8
bibliography: references.bib
---

## Commit 1

#### Library Loading

```{r}

#new computer, who dis?

#install.packages("here")
#install.packages("rio")
#install.packages("ggplot2")
#install.packages("tidyverse")
#install.packages("dplyr")

library(here)
library(rio)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(knitr)

#I loaded packages I thought we'd use, but I might have missed some. You may need to load others!

```

#### Load "star.csv" Data

```{r}

star <- import(here("data", "star.csv")) %>%
  as_tibble()

```

## Commit 2

Our team used the software R [@manual] to analyze the effect of cats on human emotion. @pongracz2018 discuss the important relationship between cats and humans, and some findings suggest that cats have a positive effect on human emotions [@bao2016; @galvan2016].

## Commit 3

```{r}
star_new <-star %>% 
 group_by(sex, frl) %>%
 summarize(math_mean = mean(tmathss),
            math_sd   = sd(tmathss),
            rdg_mean = mean(treadss),
            rdg_sd   = sd(treadss)) %>%
  select(sex, frl, math_mean, math_sd, rdg_mean, rdg_sd)


star_table <-kable(star_new)

star_table
```
Overall, the average reading scores were lower, and had a lower standard deviation than student math scores. Girls also had a  higher average score than boys in both reading and math, and had a higher standard deviation in reading compared to boys, but a lower standard deviation in math. For both boys and girls, in reading and math, those who received free and reduced lunch had a lower average score

## Commit 4 

# Create the following plot, using whatever theme you’d like, and briefly discuss it in text. (Note that might need to problem-solve how to put the legend at the bottom.)

```{r}
star <- star%>%
characterize

star <- star %>%
  mutate(frl = recode(
    frl,
    "no" = "Free/Reduced Price Meals",
    "yes" = "Paid Meals"
  ))

graph1 <- star%>%
  ggplot(aes(totexp, tmathss)) + 
  geom_point(color="gray", size = 0.5) +
  geom_smooth(aes(color=frl),method= lm) +
  theme_minimal() +
  theme(legend.position ="bottom") +
  labs(color = "Free lunch")+
  labs(x = "Teacher Experience (Years)", 
       y = "Total Math Scale Scores",
       title = "Relation between teacher experience and math scores",
       subtitle = "Separate regression lines displayed by free/reduced price lunch status")

graph1 + scale_fill_discrete(name="Free\nLunch")

```


\newpage
# References 

```{r}

  
```

